Effects of the body force on the pedestrian and evacuation dynamics

### 2020-02-07 paper.tex
puse kn y kt donde correspondia

Besides, no reliable values for the sliding friction $\kappa$ appears to be 
available in the literature (to our knowledge). We may presume, however, that 
the sliding friction approaches a fraction of the body force. We will come back 
to this issue in Section~\ref{background}. \\

@@

\begin{equation}
 \mathbf{f}_g^{(ij)}=\kappa\,g(R_{ij}-r_{ij})\,
(\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
k\,g(R_{ij}-r_{ij})\,
\,\hat{\mathbf{n}}_{ij}\label{eqn_friction}
\end{equation}

@@

The sliding friction occurs in the tangential direction while the body force 
occurs in the normal direction. Both are assumed to be linear with respect to 
the net distance between contacting pedestrians. The sliding friction is also 
linearly related to the difference between the (tangential) velocities. The 
coefficients $\kappa$ (for the sliding friction) and $k_n$ (for the 
body force) are supposed to be related to the areas of contact and the clothes 
material, among others. \\

We stress that the expression (\ref{eqn_friction}) assumes fixed values for 
$\kappa$ and $k_n$. This may not be completely true according to 
Table~\ref{table_data}. The local density (and thus, the pedestrians' 
compression) may affect the compressibility parameter $k_n$ by more than an order 
of magnitude. We will vary $k_n$ (and $\kappa$) in order to explore this 
phenomenon. \\

@@

\subfloat[\label{venn_2parameters}]
{\includegraphics[width=0.49\columnwidth]{./venn_2parameters.png}}
\hfill    
\subfloat[\label{venn_3parameters}]
{\includegraphics[width=0.49\columnwidth]{./venn_3parameters.png}
}\\
\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
appearing in the equation of motion (\ref{eqn_motion}) (see 
Appendix~\ref{appendix1} for details). The sets correspond to 
$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,\kappa\}$ and 
$\mathcal{K}_c=\{\tau/m,1/v_d,B,k\}$. (a) The Venn diagram representation if no 
body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
\label{venn_diagram}
\end{figure}

@@

Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is 
absent. Notice that $A/v_d$ or $\kappa B$ may control the collective 
dynamic, in spite of the ``assertive'' attitude. The individual character of 
$v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
``loosely'' that any numerical setting of these parameters may be 
counterbalanced by the right setting of $A$ or $\kappa$, keeping the 
colletive dynamic (qualitatively) unchanged.  \\

@@

\textcolor{red}{It is worth noting} from Fig.~\ref{degree_dens} that ``stiff''
pedestrians exhibit a sharper transition to the maximum packing density than 
the ``soft'' pedestrians. We further checked this phenomenon by counting the 
number of loops of three nodes (say, the triangles) present in the network. 
This magnitude was reported to be a sensitive magnitude for characterizing the 
jamming transition in a compressed granular packing (see 
Ref.~\cite{pugnaloni_2013} for details).  As can be seen in 
Fig.~\ref{triangles}, the ``stiff'' pedestrians share more triangles 
than the ``soft'' ones.\textcolor{red}{ The maximum number of allowed triangles is 6, 
corresponding to a hexagonal arrangement.}    \\

@@

The SFM description in section~\ref{sfm} introduces seven parameters ($m$, 
$\tau$, $v_d$, $B$, $A$, $\kappa$ and $k_n$) attaining for the ``individual'' 
behavior of each pedestrian. The collective dynamic, however, requires a 
smaller set of parameters. In order to identify this smaller set, we introduce 
the following unit-less magnitudes\\

@@

\begin{equation}
 \mathcal{A}=\displaystyle\frac{A\,\tau}{m\,v_d}\ \ \ \ , \ \ \ \ 
 \mathcal{K}=\displaystyle\frac{\kappa\,B\,\tau}{m}\ \ \ \ , \ \ \ \
 \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m\,v_d}
\end{equation}

>>>>

Besides, no reliable values for the sliding friction $k_t$ appears to be 
available in the literature (to our knowledge). We may presume, however, that 
the sliding friction approaches a fraction of the body force. We will come back 
to this issue in Section~\ref{background}. \\

@@

\begin{equation}
 \mathbf{f}_g^{(ij)}=k_t\,g(R_{ij}-r_{ij})\,
(\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
k_n\,g(R_{ij}-r_{ij})\,
\,\hat{\mathbf{n}}_{ij}\label{eqn_friction}
\end{equation}

@@

The sliding friction occurs in the tangential direction while the body force 
occurs in the normal direction. Both are assumed to be linear with respect to 
the net distance between contacting pedestrians. The sliding friction is also 
linearly related to the difference between the (tangential) velocities. The 
coefficients $k_t$ (for the sliding friction) and $k_n$ (for the 
body force) are supposed to be related to the areas of contact and the clothes 
material, among others. \\

We stress that the expression (\ref{eqn_friction}) assumes fixed values for 
$k_t$ and $k_n$. This may not be completely true according to 
Table~\ref{table_data}. The local density (and thus, the pedestrians' 
compression) may affect the compressibility parameter $k_n$ by more than an order 
of magnitude. We will vary $k_n$ (and $k_t$) in order to explore this 
phenomenon. \\

@@

\subfloat[\label{venn_2parameters}]
{\includegraphics[width=0.49\columnwidth]{./venn_2parameters.png}}
\hfill    
\subfloat[\label{venn_3parameters}]
{\includegraphics[width=0.49\columnwidth]{./venn_3parameters.png}
}\\
\caption[width=0.47\columnwidth]{Venn diagrams for the unit-less parameters
appearing in the equation of motion (\ref{eqn_motion}) (see 
Appendix~\ref{appendix1} for details). The sets correspond to 
$\mathcal{A}=\{\tau/m,1/v_d,A\}$, $\mathcal{K}=\{\tau/m,B,k_t\}$ and 
$\mathcal{K}_c=\{\tau/m,1/v_d,B,k_n\}$. (a) The Venn diagram representation if no 
body force is introduced in the SFM (only sets $\mathcal{A}$ and $\mathcal{K}$, 
as in Ref.~\cite{dorso_2019}). (b) The Venn diagram representation for the sets 
$\mathcal{A}$, $\mathcal{K}$ and $\mathcal{K}_c$. }
\label{venn_diagram}
\end{figure}

@@

Fig.~\ref{venn_2parameters} represents the situation when $\mathcal{K}_c$ is 
absent. Notice that $A/v_d$ or $k_t B$ may control the collective 
dynamic, in spite of the ``assertive'' attitude. The individual character of 
$v_d$ or $B$ appears somehow ``loosely'' in the crowd dynamic. We mean by 
``loosely'' that any numerical setting of these parameters may be 
counterbalanced by the right setting of $A$ or $k_t$, keeping the 
colletive dynamic (qualitatively) unchanged.  \\

@@

It is worth noting from Fig.~\ref{degree_dens} that ``stiff''
pedestrians exhibit a sharper transition to the maximum packing density than 
the ``soft'' pedestrians. We further checked this phenomenon by counting the 
number of loops of three nodes (say, the triangles) present in the network. 
This magnitude was reported to be a sensitive magnitude for characterizing the 
jamming transition in a compressed granular packing (see 
Ref.~\cite{pugnaloni_2013} for details).  As can be seen in 
Fig.~\ref{triangles}, the ``stiff'' pedestrians share more triangles 
than the ``soft'' ones.\textcolor{red}{ The maximum number of allowed triangles is 6, 
corresponding to a hexagonal arrangement.}    \\

@@

The SFM description in section~\ref{sfm} introduces seven parameters ($m$, 
$\tau$, $v_d$, $B$, $A$, $k_t$ and $k_n$) attaining for the ``individual'' 
behavior of each pedestrian. The collective dynamic, however, requires a 
smaller set of parameters. In order to identify this smaller set, we introduce 
the following unit-less magnitudes\\

@@

\begin{equation}
 \mathcal{A}=\displaystyle\frac{A\,\tau}{m\,v_d}\ \ \ \ , \ \ \ \ 
 \mathcal{K}=\displaystyle\frac{k_t\,B\,\tau}{m}\ \ \ \ , \ \ \ \
 \mathcal{K}_c=\displaystyle\frac{k\,B\,\tau}{m\,v_d}
\end{equation}
